### 2018-12-12 tex/abstract.tex
Abstract modified@

\begin{abstract}
    Submodular extensions of an energy function can be used to efficiently
    compute approximate marginals via variational inference. The accuracy of
    the marginals depends crucially on the quality of the submodular extension.
    To identify the best possible extension, we show an equivalence between the
    submodular extensions of the energy and the objective functions of linear
    programming (LP) relaxations for the corresponding MAP estimation problem.
    This allows us to (i) establish the worst-case optimality of the submodular
    extension for Potts model used in the literature; (ii) identify the
    worst-case optimal submodular extension for the more general class of
    metric labeling; and (iii) efficiently compute the marginals for the widely
    used dense CRF model with the help of a recently proposed Gaussian filtering method. Using synthetic and real data, we show that our approach provides comparable upper bounds on the log-partition function to those obtained using tree-reweighted message passing (TRW) in cases where the latter is computationally feasible. Importantly, unlike TRW, our approach provides the first practical algorithm to compute an upper bound on the dense CRF model.
\end{abstract}

>>>>

\begin{abstract}
    Submodular extensions of an energy function can be used to efficiently
    compute approximate marginals via variational inference. The accuracy of
    the marginals depends crucially on the quality of the submodular extension.
    To identify accurate extensions for different classes of energy functions, we show a relation between the
    submodular extensions of the energy and the objective functions of linear
    programming (LP) relaxations for the corresponding MAP estimation problem via the Lovasz extension. 
    This allows us to (i) establish the worst-case optimality of the submodular
    extension for Potts model used in the literature; (ii) identify the
    worst-case optimal submodular extension for the more general class of
    metric labeling; (iii) efficiently compute the marginals for the widely
    used dense CRF model with the help of a recently proposed Gaussian
    filtering method; and (iv) propose a good submodular extension based on an accurate LP
    relaxation for the higher-order Potts model. Using synthetic and real data, we show that our approach provides comparable upper bounds on the log-partition function to those obtained using tree-reweighted message passing (TRW) in cases where the latter is computationally feasible. Importantly, unlike TRW, our approach provides the first practical algorithm to compute an upper bound on the dense CRF model with higher-order Potts potentials.
\end{abstract}

### 2018-12-12 tex/paper.tex
Abstract modified@

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.14]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_submod} &
    %
        \includegraphics[scale = 0.19]{\imagePath/stereo/tsukuba_GT} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_mf} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_submod} \\
        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07} & {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\
         \includegraphics[scale = 0.14]{\imagePath/stereo/cones_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_submod} &
        %
       %
         \includegraphics[scale = 0.15]{\imagePath/stereo/teddy_GT} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_mf} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_submod} \\
    \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} & {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
compatibility and Gaussian pairwise potentials. We compare our solution with
the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
\label{fig:stereo}
\end{figure*}

@@

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
        {} & {} 
        & {} & \scriptsize 2476.82s
        & {} & \scriptsize 2471.58s\\

\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
\label{fig:stereo_hop}
\end{figure*}

>>>>

%\begin{figure*}
%    \centering
%\begin{tabular}{cccccc}
%        \includegraphics[scale = 0.14]{\imagePath/stereo/venus_GT} &
%        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_mf} &
%        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_submod} &
%    %
%        \includegraphics[scale = 0.19]{\imagePath/stereo/tsukuba_GT} &
%        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_mf} &
%        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_submod} \\
%        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
%        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07} & {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\
%         \includegraphics[scale = 0.14]{\imagePath/stereo/cones_GT} &
%        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_mf} &
%        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_submod} &
%        %
%       %
%         \includegraphics[scale = 0.15]{\imagePath/stereo/teddy_GT} &
%        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_mf} &
%        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_submod} \\
%    \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
%        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} & {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
%\end{tabular}
%%\vspace{2mm}
%\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
%compatibility and Gaussian pairwise potentials. We compare our solution with
%the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
%\label{fig:stereo}
%\end{figure*}

@@

%\begin{figure*}
%    \centering
%\begin{tabular}{cccccc}
%        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
%        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
%        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
%        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
%        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
%        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
%        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
%        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
%        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
%        {} & {} 
%        & {} & \scriptsize 2476.82s
%        & {} & \scriptsize 2471.58s\\
%
%\end{tabular}
%%\vspace{2mm}
%\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
%  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
%\label{fig:stereo_hop}
%\end{figure*}
%
